Hypertension and microbiome

### 2019-10-21 articletwo.Rmd
Minor

pcoa.plot <- ggplot(data=pcoa.df %>% gather(key, Axis, Axis.2, Axis.3),
                    aes(x=Axis.1, y=Axis, color = HYPERTENSION)) +
    facet_wrap(~key, scales = "free_y", strip.position = "left", labeller = axis_labeller) +
    geom_point(size=0.1, alpha=0.4) +
    xlab(sprintf("PCoA Axis 1 (%.1f%%)", 100*eig.fracs[1])) +
    ylab(NULL) +
    scale_colour_manual(name = "State and treatment",
                        labels = c("Normotensive", "Hypertensive"),
                        breaks=c(0, 1),
                        values = c("blue", "red")) +   
    scale_x_continuous(breaks=seq(-5, 5, 1)) +
    scale_y_continuous(breaks=seq(-5, 5, 1)) +
    theme_classic() +
    guides(colour = guide_legend(override.aes = list(size=4))) +
    coord_cartesian(clip = 'off') +
    theme(text = element_text(size=12),
          legend.position = c(0.35, 0.95),
          legend.title = element_blank(),
          legend.text = element_text(size = 10),
          legend.key.size = unit(5, "mm"),
          legend.background = element_blank(),
          strip.background = element_blank(),
          strip.placement = "outside",
          aspect.ratio = 1,
          strip.text = element_text(size = 14),
          axis.title.x = element_text(size = 14))

ggsave(file = "cache/pcoa-species.png", plot=pcoa.plot, height=3.4, width=6, units = "in", dpi = 300)
```

@@

First three axis explain portion (`r eig.fracs[1:3]`) of
variation. Testing associations to blood pressure variables on PCoA
axis 1

@@

```{r results compare deseq2}
map(dds3, ~sum(results(.x, name = "HYPERTENSION_1_vs_0")$padj < 0.05)) %>%
    map_df(~as.data.frame(.x) %>% dplyr::rename(qval = .x), .id = "included") %>%
    kable
```

```{r deseq continuous}
dset.deseq.signf <- deseqresults(dds, names.dset)
dset.deseq.signf %>% pull(qval) %>% length
```

@@

```{r deseq abundances for boxplot}
dset.deseq.boxplot <- pseq.genus %>%
    microbiome::transform(., transform = "compositional") %>%
    prune_taxa(unique(pull(dset.deseq.signf, Feature)), .) %>%
    psmelt %>%
    mutate(Abundance = sqrt(Abundance))
```

```{r deseq boxplot}
g.boxplot <- dset.deseq.boxplot %>%
    group_by(OTU) %>%
    mutate(outlier = abs(Abundance) > median(Abundance) + IQR(Abundance) * 1.5) %>%
    ggplot(aes(x = HYPERTENSION, y = Abundance, color = OTU)) +
    geom_boxplot(lwd=0.1, outlier.shape = NA) +
    geom_point(data = function(x) dplyr::filter_(x, ~ outlier),
               position = position_jitterdodge(jitter.width = 0.02),
               size = 0.1,
               alpha = 0.4, shape = ".") +
    scale_y_continuous(limits = c(0, 0.2), expand = c(0, 0)) +
    scale_x_discrete(labels=c("0" = "Normotensive", "1" = "Hypertensive")) +
    ylab("Abundance (Hellinger)") +
    xlab("") +
    theme_classic() +
    guides(shape = guide_legend(override.aes = list(size = 0.1)),
           color = guide_legend(override.aes = list(size = 0.1))) +
    theme(legend.title = element_text(size = 4), 
          legend.text  = element_text(size = 4),
          legend.key.size = unit(1, "lines"),
          legend.position="bottom")

ggsave(file = "cache/dds-test.png", plot=g.boxplot, height=4, width=6, units = "in", dpi = 300)
```

<img src = "cache/dds-test.png" />

>>>>

pcoa.plot <- ggplot(data=pcoa.df %>% gather(key, Axis, Axis.2, Axis.3),
                    aes(x=Axis.1, y=Axis, color = HYPERTENSION)) +
    facet_wrap(~key, scales = "free_y", strip.position = "left", labeller = axis_labeller) +
    geom_jitter(size=4, alpha=0.4, shape = ".") +
    xlab(sprintf("PCoA Axis 1 (%.1f%%)", 100*eig.fracs[1])) +
    ylab(NULL) +
    scale_colour_manual(name = "State and treatment",
                        labels = c("Normotensive", "Hypertensive"),
                        breaks=c(0, 1),
                        values = c("blue", "red")) +   
    scale_x_continuous(breaks=seq(-5, 5, 1)) +
    scale_y_continuous(breaks=seq(-5, 5, 1)) +
    theme_classic() +
    guides(colour = guide_legend(override.aes = list(size=4, shape = 19))) +
    coord_cartesian(clip = 'off') +
    theme(text = element_text(size=10),
          legend.position = c(0.35, 0.95),
          legend.title = element_blank(),
          legend.text = element_text(size = 10),
          legend.key.size = unit(5, "mm"),
          legend.background = element_blank(),
          strip.background = element_blank(),
          strip.placement = "outside",
          aspect.ratio = 1,
          strip.text = element_text(size = 12),
          axis.title.x = element_text(size = 12))

ggsave(file = "cache/pcoa-species.png", plot=pcoa.plot, height=3.0, width=6, units = "in", dpi = 300)
```

@@

First three axis explain portion (`r sum(eig.fracs[1:3])`) of
variation. Testing associations to blood pressure variables on PCoA
axis 1

@@

```{r results compare deseq2}
map(dds3, ~sum(results(.x, name = "HYPERTENSION_1_vs_0")$padj < 0.05, na.rm = TRUE)) %>%
    map_df(~as.data.frame(.x) %>% dplyr::rename(qval = .x), .id = "included") %>%
    kable
```

```{r deseq continuous}
dset.deseq.signf <- deseqresults(dds, names.dset)
```

@@
